### 2020-04-20 README.Rmd
updated readme

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, berlin.trees, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

## Purpose

This repository contains an analysis of tree growth (potential) and its relationship with the Urban Heat Island (UHI) effect in Berlin using an extensive, publicly available data set. 
For some details of the (on-going) research, download this [file](./analysis/paper/paper.html)

## Approach

The folder structure follows the principal of a [research compendium](https://research-compendium.science/) following concepts developed by [Ben Marwick and others](https://www.tandfonline.com/doi/abs/10.1080/00031305.2017.1375986?journalCode=utas20).
That means all analyses and the final write-up are organized in a (fairly) coherent manner, encouraing reproducibility.

I chose to package up the analyses in an `R` package to facilitate reproducibility, as dependencies are more easily tracked, and analyses steps can be broken down into functions that can be tested, adjusted when necessary, and most important, re-used.

<!-- [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio) -->

<!-- This repository contains the data and code for our paper: -->

<!-- > Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx> -->

<!-- Our pre-print is online here: -->

<!-- > Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

<!-- ### How to cite -->

<!-- Please cite this compendium as: -->

<!-- > Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

<!-- ### How to download or install -->

<!-- You can download the compendium as a zip from from this URL: </archive/master.zip> -->

<!-- Or you can install this compendium as an R package, berlin.trees, from GitHub with: -->

<!-- ```{r gh-installation, eval = FALSE} -->
<!-- # install.packages("devtools") -->
<!-- remotes::install_github("/") -->
<!-- ``` -->

<!-- ### Licenses -->

<!-- **Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/) -->

<!-- **Code :** See the [DESCRIPTION](DESCRIPTION) file -->

<!-- **Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse -->

<!-- ### Contributions -->

<!-- We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms. -->
